EEG2fMRI: Cross-Modal Synthesis for Functional Neuroimaging

### 2020-11-22 article/article.tex
Update Methods

The suitability of EEG-fMRI as a candidate pair for cross-modal image synthesis is supported by the established practices of multi-modal neuroimaging using EEG-fMRI. These practices are the result of physical compatibility and the presence of complementary qualities.

@@

>>>>

The suitability of EEG-fMRI as a candidate pair for supervised cross-modal synthesis is supported by the established practices of multi-modal neuroimaging using EEG-fMRI. These practices are the result of physical compatibility and the presence of complementary qualities.

@@

\section{Methods}
